\pdfinfo{
   /Author (Caleb Callaway)
   /Title (Resume)
   /CreationDate (D:19700101000000)
   /ModDate (D:19700101000000)
}
\pdftrailerid{}

\documentclass{article}
\pagestyle{empty}

\renewcommand{\familydefault}{\sfdefault}

\usepackage[letterpaper, portrait, textheight=10in, top=.5in]{geometry}

\usepackage[bookmarks=false,pdfborder={0 0 0}]{hyperref}
\hypersetup{colorlinks,urlcolor=[RGB]{17, 85, 204}}

\usepackage{titlesec}
\titleformat{\section}
	{\large\bf}{}{}{}[{\vspace{-.25pc}\titlerule\vspace{-.5pc}}]

\usepackage{enumitem}
\setlist{noitemsep}

\usepackage{soul}
\setul{1pt}{.4pt}

\begin{document}
	\begin{center}
		{\Large Caleb Callaway}\\
		\href{mailto:cqcallaw@brainvitamins.net}{\ul{cqcallaw@brainvitamins.net}}\\
		\href{http://linkedin.com/in/cqcallaw/}{\ul{linkedin.com/in/cqcallaw}} . \href{https://github.com/cqcallaw/}{\ul{github.com/cqcallaw}}\\
		\href{https://www.brainvitamins.net/}{\ul{www.brainvitamins.net}}
	\end{center}

	\section*{Objective}
	\indent{Design, implement, and deliver excellent solutions to practical problems.}

	\section*{Skillset}
	\begin{itemize}[label={}]
		\item GPU Development, Debug, and Performance Analysis
		\item Scripting and Automation (Bash, Python)
		\item Software development (C++, past experience with C\# and Java)
		\item Linux System Administration (Samba, LDAP, Kerberos, Single Sign-On, Backup Procedures)
	\end{itemize}

	\section*{Work History}
	\begin{description}
		\item[{[}2016-present{]} Graphics Engineer at \href{http://www.intel.com/}{\ul{Intel Corporation}}] \hfill \\
		Benchmarking, analysis, and debug of 3D and compute workloads. Emphasis on Linux driver stack since 2019.
		\item[{[}2015{]} Graphics Architecture Lab Execution Internship at \href{http://www.intel.com/}{\ul{Intel Corporation}}] \hfill \\
		Summer internship (June through August) analyzing current and next-generation graphics hardware performance while developing software tools to support performance analysis.
		\item[{[}2008-2014{]} Software development and IT at \href{http://www.autometrix.com/}{\ul{Autometrix Precision Cutting Systems}}] \hfill \\
		Design, implementation, deployment and maintenance of CAD software applications and CNC control software (C\#, WPF, C++, Forth). Design and maintenance of internal network (Linux and Windows Server administration). Primary maintainer of company website; primary coder of 2009 website re-design (XHTML, CSS, PHP).
		\item[{[}2006-2010{]} Installations and customer service at \href{http://www.autometrix.com/}{\ul{Autometrix Precision Cutting Systems}}] \hfill \\
		Domestic and international installation of flatbed CNC cloth-cutting systems and software. Domestic and international customer service, training, and technical support. Product documentation and document control.
		\item[{[}2000-2005{]} Site Coordinator for GameSpy Networks' Deus Ex fansite \href{http://planetdeusex.com}{\ul{planetdeusex.com}}] \hfill \\
		Community leadership through management of an international volunteer staff and forum administration. Maintenance of the website's codebase. News reporting and content development.
	\end{description}

	\section*{Contributions}
	\begin{description}
		\item[newt: \href{https://github.com/cqcallaw/newt}{\ul{github.com/cqcallaw/newt}}] \hfill \\
		Type-safe, immutability-first programming language.
		\item[Kerberos Guide: \href{https://help.ubuntu.com/community/Kerberos}{\ul{help.ubuntu.com/community/Kerberos}}] \hfill \\
		Comprehensive Kerberos server and client configuration wiki article.
		\item[Kerberos on Android: \href{https://github.com/cqcallaw/kerberos-app/}{\ul{github.com/cqcallaw/kerberos-app}}] \hfill \\
		UI overhaul and support for password conversations, using C, JNI, and Android-flavored Java.
		\item[RFID PAM authentication module: \href{http://sourceforge.net/projects/pam-phidgetrfid/}{\ul{sourceforge.net/projects/pam-phidgetrfid}}] \hfill \\
		Design and implementation of a Linux PAM module in C, gaining experience with the Linux PA architecture, third-party device drivers, Autotools, splint, and Ubuntu/Debian packaging.
	\end{description}

	\section*{Education}
	\begin{description}
		\item[{[}2016{]} Bachelor of Science, Computer Science, \href{http://www.csuchico.edu/}{\ul{California State University, Chico}}] \hfill \\
		Graduated with Honors and {\em magna cum laude}.
		\item[{[}2007{]} Associate of Science, Computer Science, \href{http://www.sierracollege.edu/}{\ul{Sierra College, Rocklin, CA}}] \hfill \\
		Graduated with Honors.
	\end{description}
	Major GPA: 3.9

	\section*{Interests}
	Well-engineered solutions to practical problems; communication security; software freedom
\end{document}
